\chapter{Discussion and Conclusion}

In the SOFR studies, we examined the implications of different underlying calculation methods for the SOFR futures. We studied a 3M-arithmetic product: 
\[
X^{3M_{A}}(S,T) = \frac{1}{T-S}\int_{S}^{T}r_{u}du
\]
Against taking  a $\hat{a}_{t}-f^{3M}(t,S,T)$ 3M-SOFR futures position vs \\ 
taking  a $(\hat{a}_{t}, \hat{b}_{t}, \hat{c}_{t})-f^{1M}(t,S,T)$ 1M-SOFR futures position.  
\\~\\
For simulation purposes, we chose the following model for the integral of $r = (r(t))_{t\geq 0}$: 
\begin{align*}
\int_{S}^{T}r(u)du 
&= 
\left(
\frac{r(t)-m}{\alpha}
\right)
\left[
e^{-\alpha(S-t)} - e^{-\alpha(T-t)}
\right]
+ m(T-S) 
+ 
\frac{\sigma}{\alpha}\int_{t}^{T}\Sigma(u,t,S,T)dW^{Q}(u)   
\end{align*}
Where: 
\begin{align*}
\Sigma(u,t,S,T) &= 
\left[
e^{-\alpha(S-u)}-e^{-\alpha(T-u)}
\right]\mathbbm{1}_{[t,S)}(u) 
+ 
\left[
1-e^{-\alpha(T-u)}
\right]\mathbbm{1}_{[S,T]}(u)
\end{align*}

It should be mentioned that this may not be a realistic representation of $r$, and should be addressed accordingly. As mentioned in \cite{brigo2013interest}, a solution could be multi-factor models, as one source of uncertainty could be too restrictive for realistic modelling approaches.
\\~\\
In \cite{Skov_2020}, they consider 1-, 2- and 3-factor versions of Gaussian arbitrage-free short-rate models. One should also take into account the market price of risk $\lambda_{t}$, coming from Girsanov's Theorem: $dW^{Q}(t) = dW(t) - \lambda_{t}dt$, to get suitable  $P$-dynamics of the futures rates: $f^{\ell M}, \ell = 1,3$
\\~\\
From simulations we got $\hat{a}_{t}^{3M} = 0.95$ for the position in 3M-SOFR futures. An ideal hedge here would be if this number equalled $1$. Pretend that instead of hedging $X^{3M_{A}}(S,T)$, we wanted to hedge: 
\begin{align*}
X^{3M_{G}}(S,T) := \frac{1}{T-S}\left[
e^{\int_{S}^{T}r(u)du}-1
\right]    
\end{align*}

Namely a geometric average over the period $[S,T]$, then: 
\begin{align*}
G(a_{t}) := \argmin\limits_{a_{t} \in \R}\E_{Q}\left[
\left(
X^{3M_{G}}(S,T)-a_{t}f^{3M}(t,S,T)
\right)^{2}
\bigg{|}\F_{t}
\right]
\end{align*}

Now following the same arguments as on p.\pageref{result: optimal_SOFR_hedge_3MA_vs_3GM}, we get: 
\begin{align*}
\hat{a}_{t}^{3M} &= \frac{
\E_{Q}[X^{3M_{G}}(S,T)|\F_{t}]
}{
f^{3M}(t,S,T)
}
= 
\frac{
f^{3M}(t,S,T)
}{
f^{3M}(t,S,T)
} = 1
\end{align*}


\newpage 
We imposed a model for ESG-linked swaps, which lead to a sequence of fixed rates $\kappa_{t}^{ESG}  = (\kappa_{t}^{ESG}(i))_{i=1}^{n}$ giving a penalty/discount depending on whether the criteria were met or not.
\\~\\ 
We remember that the criteria $A_{i}$ looked like the following:
\begin{align*}
A_{i} &= \{X_{T_{i}} \leq C_{T_{i}}^{ESG}\}    
\end{align*}

This means that our ESG-fixed rate process heavily depends upon the OU-process $X(t)$ and the criteria $C_{T_{i}}^{ESG}$. It could be hard to establish "reasonable" criteria. In our simulation, we took $C^{ESG} = (C_{T_{i}}^{ESG})_{i\geq 1}$ to be $\F_{0}$-measurable, this could lead to some uncertainty as one would have to "know" even more about the company's development. Maybe a more reasonable approach would be to take $C^{ESG}$ to be $\F_{T_{i-1}}$-measurable. However, this would require a model for $C^{ESG}$, which adds to the complexity again.    
\\~\\
In our modelling approach, we modelled directly under $Q$. However, the market one operates in is under $P$, meaning that it would have been suitable with an Esscher-transform of $X(t)$, which then by  Proposition \ref{prop: Esscher_transform_CPP_Q} means that we would still have a CPP, but with altered intensity $\lambda_{Q}$ and jump-size distribution $F_{J}^{Q}(dx)$.
\\~\\
In our case we have $I(t) = \sum_{k=1}^{N(t)}J_{k}$ with $N(t) \sim Pois(\lambda t)$ and 
$J\sim Exp(\mu)$, and from Lemma \ref{lemma: CPP_exp_mu}, with $\theta \in (-\infty, \mu)$, we have:
\begin{align*}
\lambda_{Q} &= \frac{\lambda \mu}{\theta - \mu} \;\text{and}\;
J \stackrel{Q}{\sim} Exp(\mu - \theta)
\end{align*}

Furthermore, $X(t)$ is company dependent, meaning that to get reasonable estimates of the necessary parameters included, data accessibility is crucial to impose a suitable model. 
\\~\\ 
One should also mention that many ESG-rating agencies have different metrics for measuring the ESG score/risk score. These metrics are not necessarily standardized, and it can be unclear how the rating firm weighs the "E", "S", and "G". Should "E" be more "important" than "S" or "G"? 
\\~\\
If one looks at the expression $K_{n}^{ESG}(\omega)$: 
\begin{align*}
K_{n}^{ESG}(\omega) &= 
[\kappa -dn]\mathbbm{1}\left[
\bigcap_{i\in \mathcal{I}_{n}}A_{i}
\right](\omega) \\ 
&+ 
\sum_{\alpha \in \mathcal{I}_{2n}^{Even}}
\left(
[\kappa -d(n-\alpha)]\mathbbm{1}\left[
\bigcup_{
j_{1}\neq \dots \neq j_{|\mathcal{I}_{\alpha}^{Even}|}
\in \mathcal{I}_{n}
}\left(
\bigcap_{i\in \mathcal{I}_{n}}A_{i}
\right)^{
\{
(j_{1}, \dots , j_{|\mathcal{I}_{\alpha}^{Even}|})
\}
}
\right]
\right)(\omega) 
\end{align*}

We see that it tracks every path, and for each $n$ there are $2^{n}$-possible paths, meaning that as $n$ increases, the complexity increases. Furthermore, this expression is rather general, meaning that one must rely upon Monte Carlo simulations to get an estimate of $\kappa_{t}^{ESG}(i)$. At the same time, it also gives possibilities for other types of stochastic models for the ESG-risk score. 




%\label{discussion}
%\kant[15] % Dummy text
%\section{All my great results}
%\kant[16]
%\paragraph{List with bullets}
%\begin{itemize}
%    \item This is a list with bullets - the symbol can be %changed easily.
%     \item[!] A point to exclaim something!
%  \item[$\blacksquare$] Make the point fair and square.
%  \item[] A blank label?
%    \item This is the last item.
%\end{itemize}
%\paragraph{Numbered lists}
%\begin{enumerate}
%    \item This is a numbered list.
%     \item This is the second item.
%\end{enumerate}
%\paragraph{Descriptions}
%\begin{description}
%\item[My first great result] This is a description list.
% \item[My second great result] This is the second item.
%\end{description}
%\section{Pros and cons}
%\kant[17]
%\section{Future research}
%\kant[18]